Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-07 report/report.tex
Divide the background into subsections

\section{Background of 3D City Representation}

@@

\section{Related work}
Van Oorts criteria for evaluating the quality of geographical information, which at the time of publication received attention from surveyors and cartographers. (van Oort, 2006)

>>>>

\subsection{Background of 3D City Representation}

@@

\subsection{Related work}
Van Oorts criteria for evaluating the quality of geographical information, which at the time of publication received attention from surveyors and cartographers. (van Oort, 2006)
